### 2014-10-08 ApTranscriptome_TR.Rmd
updates to analysis

### predicted values
resp.TPM.dt.sub.pred[,pTPM.scaled:=scale(pTPM), by = Transcript]

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, resp.TPM.dt.sub.pred, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))
```

>>>>

### predicted values
resp.TPM.dt.sub.pred[,pTPM.scaled:=scale(pTPM), by = Transcript]
setkey(resp.TPM.dt.sub.pred, "Transcript")

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(TPM.dt.sub, RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, hsp_responsive, hsp_all, mh.test, mh_plot, Ap.BP.resultParentChild, resp.stress.responsive.count, T_on.high.ttest, T_on.low.ttest, T_off.int.high.ttest, T_off.int.low.ttest, Ap.gsea.intersect, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, Ar.int.A22.lowbim.gsea, quadratic.lms, resp.TPM.dt.sub.pred, md, file = paste("doc/ms_", Sys.Date(), ".RData", sep = ""))
```
